\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-28 paper.tex
Update on Overleaf.
[broadcasted->broadcast]

Work on distributed scene graphs~\cite{naef2003blue} has been previously applied
to robotics to provide a shared 3D representation of the robot's environment
(for instance, the \emph{Robot Scene Graph}~\cite{blumenthal2013scene} or the
\emph{Deep State Representation} proposed in~\cite{bustos2016unified}).  \uwds
offers a similar distribution mechanism for 3D scene graphs and extends it to
temporal representations. Besides, \uwds further extends this line of work by
providing the ability to create, manipulate and share \emph{multiple alternative
worlds}. As an example, these could correspond to filtered or hypothetical \emph{views} on
the initial, perceived model of the environment.

@@

% JK: like software, the plural of middleware is middleware :)
Traditional robotic middleware, like ROS, is not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are
not first-class citizens (a basic task like displaying a 3D mesh at a dynamic
position is not particularly easy to perform with ROS) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.

@@

Clients can both read and write onto the worlds they are connected to, and
automatically see updates broadcasted by other clients connected to the same
world.

@@

Critically, the network is essentially hidden to the client: from the user
perspective, the environment model is manipulated as a local data structure (see
Listing~\ref{lst|pythonapi}). Modifications to the model are asynchronously synchronised with
a central server (the {\tt underworlded} daemon) and broadcasted to every other
client connected to the same world.
% JK: underworlded - intentional? (I guess yes, but checking)

@@

This tool also supports basic object manipulations, that are broadcasted to the
other \uwds clients connected to the same world.

>>>>

%CDW - Remove 'Besides'. I think you are trying to establish why uwds is not like previous work but I don't think that word quite works in there. Probably ok with just removing it.
Work on distributed scene graphs~\cite{naef2003blue} has been previously applied
to robotics to provide a shared 3D representation of the robot's environment
(for instance, the \emph{Robot Scene Graph}~\cite{blumenthal2013scene} or the
\emph{Deep State Representation} proposed in~\cite{bustos2016unified}).  \uwds
offers a similar distribution mechanism for 3D scene graphs and extends it to
temporal representations. Besides, \uwds further extends this line of work by
providing the ability to create, manipulate and share \emph{multiple alternative
worlds}. As an example, these could correspond to filtered or hypothetical \emph{views} on
the initial, perceived model of the environment.

@@

% JK: like software, the plural of middleware is middleware :)
% CDW: I get the analogy with first-class citizens but perhaps better to replace with something like 'but is not a great strength' or 'but is not a highly developed feature'
Traditional robotic middleware, like ROS, is not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are
not first-class citizens (a basic task like displaying a 3D mesh at a dynamic
position is not particularly easy to perform with ROS) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.

@@

Clients can both read and write onto the worlds they are connected to, and
automatically see updates broadcast by other clients connected to the same
world.

@@

Critically, the network is essentially hidden to the client: from the user
perspective, the environment model is manipulated as a local data structure (see
Listing~\ref{lst|pythonapi}). Modifications to the model are asynchronously synchronised with
a central server (the {\tt underworlded} daemon) and broadcast to every other
client connected to the same world.
% JK: underworlded - intentional? (I guess yes, but checking)

@@

This tool also supports basic object manipulations, that are broadcast to the
other \uwds clients connected to the same world.
